---
title: "Netflix Siblings"
author: "Taylor Blair"
date: "1/26/2021"
output: pdf_document
urlcolor: blue
knit: (
  function(inputFile, encoding) { 

    pSubTitle <- 'Knitted Comparison'

    rmarkdown::render( 
      input       = inputFile, 
      encoding    = encoding, 
      params      = list(sub_title = pSubTitle),      
      output_file = pSubTitle) })
---

```{r setup, include=FALSE, warning=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Background

My sister and I have a long history of watching Netflix.

There are some minor outliers in the datasets, namely when we use each others accounts.

*If you would like to create your own version of this dataset, or find your Netflix history go to:* [https://www.netflix.com/YourAccount](https://www.netflix.com/YourAccount)

*From there, select the specific profile* $\boldsymbol{\Rightarrow}$ **Viewing Activity** $\boldsymbol{\Rightarrow}$ **Download All**

# Loading Libraries and Data


```{r, warning=FALSE, error=FALSE, results="hide", message=FALSE}
library(tidyverse)
library(openair)
library(readr)
```

```{r message=FALSE}
my_history <- read_csv("~/Coding/R/sis-and-me-netflix/Data/MyNetflixHistory.csv")
sibling_history <- read_csv("~/Coding/R/sis-and-me-netflix/Data/SisNetflixHistory.csv")

sample_n(my_history, 4)

```

---

# Data Prep

As can be seen above, the initial dataset contains only two variables. 

## Date fixing
```{r}
my_history$Date <- as.Date(my_history$Date,"%m/%d/%y")
sibling_history$Date <- as.Date(sibling_history$Date,"%m/%d/%y")

```


## Movie or TV series
```{r}
my_history$type <- grepl(":", my_history$Title)
my_history$type <- my_history$type %>%
  replace(my_history$type==TRUE, "TV Series") %>%
  replace(my_history$type==FALSE, "Movie")

sibling_history$type <- grepl(":", sibling_history$Title)
sibling_history$type <- sibling_history$type %>%
  replace(sibling_history$type==TRUE, "TV Series") %>%
  replace(sibling_history$type==FALSE, "Movie")

```

## Series, Season and episode

```{r, warning=FALSE, error=FALSE, results="hide"}
my_history <- my_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")

sibling_history <- sibling_history %>%
  separate(Title,
           c("Series", "Season", "Episode"),
           ": ")

```


## Day of Week
Using
```{r}
day_of_week <- function(x){
  return (weekdays(x))
}

days <- c("Monday", "Tuesday", "Wednesday", "Thursday", "Friday", "Saturday", "Sunday")

my_history$day <- sapply(my_history$Date, day_of_week)
my_history$day <- factor(my_history$day, 
                         levels = days)

sibling_history$day <- sapply(sibling_history$Date, day_of_week)
sibling_history$day <- factor(sibling_history$day, 
                              levels = days)


```

## Outputted Tibble

```{r}
sample_n(my_history, 4)

```

---

#Compare dataset

```{r}
my_history$individual <- "Tay"
sibling_history$individual <- "Sis"

merged <- rbind(my_history, sibling_history)



```

---

# Numerical analysis


## Binge Watching

Who hasn't binge watched Netflix before

```{r}

```

---

# Graphical Analysis

Looking at 

```{r}
ggplot(merged, aes(x = day, fill=individual) ) +
  geom_bar(position = "dodge") +
  labs(title = "Sis v. Tay: Netflix Shows Watched by Day") +
  scale_fill_manual("Individual", values=c("#E50914","#221F1F")) +
  xlab("Day of Week") +
  ylab("Number of Episodes Watched")

```

## A Calander of Events

2020 was a unique year, with lockdown beginning in February...

```{r}

my_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
             year = 2020)

sibling_history %>%
  group_by(Date) %>%
  summarise(count = n()) %>%
  rename(date=Date) %>%
  calendarPlot(pollutant = "count",
              year = 2020,
              month = c(1:12))


```
